---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  out.width = "75%",
  dpi = 300
)
```

# ggorbisant

Colour palettes and plotting themes for Orbisant Analytics website

## Installation

You can install `ggorbisant` from GitHub by running the following:

```{r eval = FALSE}
# install.packages("remotes")
remotes::install_github("hendersontrent/ggorbisant")
```

## Theme Orbisant

The theme works by adding the function call to the end of your `ggplot2` code:

```{r echo = TRUE, results = 'hide'}
library(ggplot2)
library(ggorbisant)

ggplot(university_enrolments, aes(x = domestic, y = international)) +
  geom_point() +
  theme_orbisant()
```

The colour palette built into the package is presented below:

```{r}
library(scales)
library(ggorbisant)

scales::show_col(ggorbisant:::orbisant_palette)
```

## This palette can be used for colouring (and filling) plots

Use `scale_colour_orbisant()` to apply the theme for colour parameters.

```{r}
library(ggplot2)
ggplot(university_enrolments, aes(x = domestic, y = international, colour = state)) +
geom_point() +
labs(title = "Go8 domestic vs international enrolments") +
scale_colour_orbisant() +
theme_orbisant()
```

And `scale_fill_orbisant()` to apply the theme for fill parameters.

```{r}
library(ggplot2)
ggplot(university_enrolments, aes(x = domestic, colour = state)) +
geom_col() +
labs(title = "Go8 domestic enrolments") +
scale_fill_orbisant() +
theme_orbisant()
```

## Data

`ggorbisant` comes with one in-built data set, which is domestic and international student enrolments for the Group of Eight (Go8) research-intensive universities in Australia.

```{r}
library(ggorbisant)

university_enrolments
```
